Experiments with Housing Data

### 2022-08-09 dev/notebooks/gravitational_generator.qmd
small change to default params for gravitational generator

```{julia}
idx = 2
x1,x2 = generators[idx].centroid[1], generators[idx].centroid[2]
plt1 = plot(counterfactuals[idx], plot_up_to=minimum([T,T_]), title="Simple")
scatter!(plt1, [x1], [x2], colour=:purple, label="attractor")
plt2 = plot(counterfactuals_strict[idx], plot_up_to=minimum([T,T_]), title="Strict")
scatter!(plt2, [x1], [x2], colour=:purple, label="attractor")
plt = plot(plt1, plt2, size=(850,350), layout=(1,2))
savefig(plt, joinpath(www_path,"gravitational_generator_comparison.png"))
```

>>>>

```{julia}
idx = 1
x1,x2 = generators[idx].centroid[1], generators[idx].centroid[2]
plt1 = plot(counterfactuals[idx], plot_up_to=minimum([T,T_]), title="Simple")
scatter!(plt1, [x1], [x2], colour=:purple, label="attractor")
plt2 = plot(counterfactuals_strict[idx], plot_up_to=minimum([T,T_]), title="Strict")
scatter!(plt2, [x1], [x2], colour=:purple, label="attractor")
plt = plot(plt1, plt2, size=(850,350), layout=(1,2))
savefig(plt, joinpath(www_path,"gravitational_generator_comparison.png"))
```
